---
title: "Quickstart Guide: zzpower"
author: "Ronald (Ryy) G. Thomas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart Guide: zzpower}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Overview

**zzpower** is an interactive Shiny application for power analysis and sample
size calculations in clinical trials. The package supports multiple statistical
tests through a scalable plugin architecture.

## Installation

```{r install}
# Install from GitHub
devtools::install_github("rgt47/zzpower")
```

```{r load}
library(zzpower)
```

## Basic Usage

Launch the interactive application:

```{r launch}
launch_zzpower()
```

The application opens in your web browser with a tabbed interface for different
statistical tests.

## Supported Statistical Tests

### Two-Group t-test (Independent Samples)

For parallel-group clinical trial designs:

- Effect size methods: Cohen's d, percent reduction, difference in scores
- Design features: dropout rates, unequal allocation ratios
- Output: power curves, sample size tables, downloadable reports

### Paired t-test

For before-after or crossover designs:

- Effect size: Standardized mean difference
- Sample size calculation for matched pairs

### One-Sample t-test

For comparison against a fixed reference value:

- Effect size: Cohen's d
- Single-group sample size determination

### Two Proportions

For binomial outcome comparisons:

- Effect size methods: two proportions, difference, odds ratio, relative risk
- Sample size calculation for binary endpoints

### Correlation Test

For bivariate relationship testing:

- Effect size: correlation coefficient (r)
- Sample size for detecting correlations

## Workflow Example

### 1. Launch Application

```{r workflow-launch}
launch_zzpower()
```

### 2. Select Test Type

Choose the appropriate tab for your study design (e.g., "Two-Group t-test").

### 3. Set Sample Size

Use the slider to set your planned total sample size.

### 4. Specify Effect Size

Choose an effect size method and set the range to evaluate:

- **Cohen's d**: Direct standardized effect (0.2 = small, 0.5 = medium, 0.8 = large)
- **Percent Reduction**: Effect as percentage reduction from control
- **Difference in Scores**: Absolute difference in outcome units

### 5. Configure Design

Adjust advanced settings:

- Dropout/drop-in rates
- Allocation ratio (1:1, 2:1, etc.)
- Alpha level (0.05, 0.01, etc.)
- One-sided vs two-sided testing

### 6. Review Results

Examine the interactive outputs:

- Power curve showing power vs effect size
- Results table with exact values
- Study design summary

### 7. Download Report

Generate a report documenting your power analysis in text or HTML format.

## Function Reference

| Function | Purpose |
|:---------|:--------|
| `launch_zzpower()` | Launch interactive Shiny app |

## Key Parameters for launch_zzpower()

| Parameter | Description | Default |
|:----------|:------------|:--------|
| `port` | Port number | NULL (random) |
| `host` | IP address | "127.0.0.1" |
| `launch.browser` | Open browser | TRUE |

## Architecture

zzpower uses a scalable plugin/registry architecture:

- **Registry**: Central specification of all test definitions
- **Generic UI Builder**: Dynamic UI generation from specifications
- **Generic Server Factory**: Dynamic server logic from specifications

This architecture enables support for 20+ statistical tests with minimal code
duplication.

## Dependencies

- shiny: Web application framework
- bslib: Bootstrap 5 theming
- pwr: Power analysis calculations
- ggplot2: Visualization
- DT: Interactive tables

## Next Steps

For detailed information on the framework architecture, see the package
documentation and CLAUDE.md.
